---
title: "Homework 2 - Q4"
author: "Srijan K. Pal"
date: "2023-02-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

9.(a)
```{r}
Auto = read.csv("Auto.csv", header=T, na.strings = "?")
Auto = na.omit(Auto)
summary(Auto)
```

```{r}
names(Auto)
pairs(Auto[,0:8])
```

9.(b)
```{r}
cor(Auto[,0:8])
```

9.(c)
```{r}
lm.fit_1=lm(mpg~.-name, data=Auto)
summary(lm.fit_1)
```
i. There is a relationship between th predictor and the response. None of the predictor coefficients are zero. The F-statistic value is much larger than 1 and the p-value is close to zero, indicating null-hypothesis testing to be false.

ii. The p-value of cylinders, horsepower, and acceleration are significantly high proving they very little statistical significance. Whereas, the p-values of displacement, weight, year and origin are significantly low proving they have high statistical significance in predicting mpg.

iii. The regression coefficient of year (0.7508) suggests that the it has a positive relationship with the response(mpg). And also the standard error is not that low so there is very little chance that the coefficient is 0. The coefficient suggests that with after approximately 7.5 year, the mpg of the car is increased by 10.


9.(d)
```{r}
attach(Auto)
par(mfrow=c(2,2))
plot(lm.fit_1)
```

The fit is not totally correct as there is non-linearity in the data. From the leverage plot, point 14 appears to have high leverage, although not a high magnitude residual.

```{r}
plot(predict(lm.fit_1), rstudent(lm.fit_1))
#abline(lm.fit_1)
```

From the studentized residual plots, it is clearly visible that there is high possibility that the data contain outliers as the some of the data points have values greater than 3.


9.(e)
```{r}
lm.fit_2 = lm(mpg~cylinders*displacement+acceleration:origin+acceleration)
summary(lm.fit_2)
```
Based on the high p-values it can be concluded that the interaction term acceleration:origin and also the acceleration term alone are not statistically significant in the above linear regression model in predicting the mpg. while the interaction term of cylinders:displacement is statistically significant with a p-value close to zero.

9.(f)
```{r}
lm.fit_3 = lm(mpg~log(year)+sqrt(acceleration)+horsepower+I(cylinders^2))
summary(lm.fit_3)
```

```{r}
par(mfrow=c(2,2))
plot(lm.fit_3)
```

```{r}
plot(predict(lm.fit_3), rstudent(lm.fit_3))
```

Apparently, from the p-values the log(year), sqrt(acceleration), horsepower and cylinders^2 all have statistical significance. The studentized plot concludes that there may be possible outliers in the data with values greater than 3. The leverage point indicate that there are only one single point with high leverage.
