---
title: "Homework 3 - Q5"
author: "Srijan K. Pal"
date: "2023-03-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Q10.(a)
```{r}
library(ISLR)
summary(Weekly)
```

```{r}
pairs(Weekly)
```

```{r}
cor(Weekly[,-9])
```

Year and Volume seems to have a relationship.

10.(b)
```{r}
glm.fit = glm(Direction~.-Today-Year, data = Weekly, family = binomial)
summary(glm.fit)
```

Lag2 appears to have some statistical significance with a low Pr(>|z|) = 0.0296.

10.(c)
```{r}
attach(Weekly)
glm.probs = predict(glm.fit, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs>0.5] = "Up"
table(glm.pred, Direction)
```

Correct predictions % = (54+557)/(54+48+430+557)=56.1%.

Weeks the market goes up the logistic regression is right most of the time, 557/(557+48) = 92.1%. 

Weeks the market goes up the logistic regression is wrong most of the time, 54/(430+54) = 11.2%.

10.(d)
```{r}
train = (Year<2009)
Weekly.0910 = Weekly[!train, ]
glm.fit = glm(Direction ~ Lag2, data = Weekly, family = binomial, subset = train)
glm.probs = predict(glm.fit, Weekly.0910, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs > 0.5] = "Up"
Direction.0910 = Direction[!train]
table(glm.pred, Direction.0910)
```

```{r}
mean(glm.pred == Direction.0910)
```

10.(e)
```{r}
library(MASS)
lda.fit = lda(Direction ~ Lag2, data = Weekly, subset = train)
lda.pred = predict(lda.fit, Weekly.0910)
table(lda.pred$class, Direction.0910)
```

```{r}
mean(lda.pred$class == Direction.0910)
```

10.(f)
```{r}
library(MASS)
qda.fit = qda (Direction ~ Lag2, data = Weekly, subset = train)
qda.class = predict(qda.fit, Weekly.0910)$class
table(qda.class, Direction.0910)
```

```{r}
mean(qda.class == Direction.0910)
```

10.(g)
```{r}
library(class)
train.X = as.matrix(Lag2[train])
test.X = as.matrix(Lag2[!train])
train.Direction = Direction[train]
set.seed(1)
knn.pred = knn(train.X, test.X, train.Direction, k = 1)
table(knn.pred, Direction.0910)
```

```{r}
mean(knn.pred == Direction.0910)
```

10.(h) Logistic regression and LDA methods provide similar test error rates.

10.(i) 

Logistic regression with Lag1, Year*Lag2 and Year:Volume
```{r}
glm.fit = glm(Direction ~ Lag1+Year*Lag2+Year:Volume, data = Weekly, family = binomial, subset = train)
summary(glm.fit)
```

```{r}
glm.probs = predict(glm.fit, Weekly.0910, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs > 0.5] = "Up"
Direction.0910 = Direction[!train]
table(glm.pred, Direction.0910)
```

```{r}
mean(glm.pred == Direction.0910)
```

LDA with Lag2 interaction with Lag1, Year*Lag2 and Year:Volume
```{r}
lda.fit = lda(Direction ~ Lag1 + Year * Lag2 + Year:Volume, data = Weekly, subset = train)
lda.pred = predict(lda.fit, Weekly.0910)
mean(lda.pred$class == Direction.0910)
```

```{r}
qda.fit = qda(Direction ~ Lag2 + sqrt(abs(Lag1)) + Year, data = Weekly, subset = train)
qda.class = predict(qda.fit, Weekly.0910)$class
table(qda.class, Direction.0910)
```

```{r}
mean(qda.class == Direction.0910)
```


KNN with k =10
```{r}
knn.pred = knn(train.X, test.X, train.Direction, k = 5)
table(knn.pred, Direction.0910)
```

```{r}
mean(knn.pred == Direction.0910)
```

KNN with k = 20
```{r}
knn.pred = knn(train.X, test.X, train.Direction, k = 20)
table(knn.pred, Direction.0910)
```

```{r}
mean(knn.pred == Direction.0910)
```
