---
title: "Homework 2 - Q3"
author: "Srijan K. Pal"
date: "2023-02-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

8.(a)

```{r}
Auto = read.csv("Auto.csv", header=T, na.strings = "?")
Auto = na.omit(Auto)
summary(Auto)
```

```{r}
names(Auto)
```

```{r}
lm.fit=lm(mpg~horsepower, data=Auto)
summary(lm.fit)
```
i. The relationship between horsepower and mpg is negative.Since the p-value of the coefficient of horsepower is close to zero and the F-statistic value is much larger than 1 and the p-value is close to zero, the relationship between horsepower and mpg is statistically very significant.

ii. The relationship between the predictor (horsepower) and the response(mpg) is negative. The Residual standard error of the fit is 4.0906 which indicates an error percentage of 20.9248% (RSE/mean mpg = 4.906/23.4459). The R^2 value of the fit is 0.6059, which signifies that 60.59% of the variance in mpg was explained by horsepower in the regression.

iii. The relationship between the predictor (horsepower) and the response(mpg) is negative.

iv.
```{r}
predict(lm.fit, data.frame(horsepower=c(98)),
        interval='confidence')
```
```{r}
predict(lm.fit, data.frame(horsepower=c(98)), 
        interval= 'prediction')
```


8.(b)
```{r}
attach(Auto)
plot(horsepower,mpg)
abline(lm.fit)
```

8.(c)
```{r}
par(mfrow = c(2,2))
plot(lm.fit)
```

The plots show their might be a non-linear relationship in the dataset between the predictor and the response.
