---
title: "Homework 2 - Q5"
author: "Srijan K. Pal"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


10.(a)
```{r}
library(ISLR)
summary(Carseats)
```

```{r}
lm.fit_1 = lm(Sales~Price+Urban+US, data=Carseats)
summary(lm.fit_1)
```
10.(b) Price - The relationship between Price and Sales is negative. The p-value is close to zero and thus, Price has statistical significance in prediction of sales.

UrbanYes - The relationship between UrbanYes and sales is negative. Although the value of the standard error is also high. The high p-value of the UrbanYes suggests that it has very little statistical significance in prediction of Sales.

USYes - The relationship between USYes and sales is positive. The p-value is close to zero and thus, USYes has statistical significance in prediction of sales. 

10.(c) Model: Sales = 13.0434 + (-0.0545)Price + (-0.0219)UrbanYes + (1.2005)USYes
 
10.(d) Based on the low p-values, null-hypothesis can be rejected for both Price and USYes.

10.(e)
```{r}
lm.fit_2 = lm(Sales~Price+US, data=Carseats)
summary(lm.fit_2)
```

10.(f) Based on the RSE and R-squared value of the linear regression, both the regression models fit similarly to the data, although the model in (e) fits the data slightly better.

10.(g)
```{r}
confint(lm.fit_2)
```

10.(h)
```{r}
plot(predict(lm.fit_2), rstudent(lm.fit_2))
```

All the studentized residuals are within the limit of -3 to 3, which typically is considered to be region beyond which outliers fall. Thus, there might not be any potential outliers from the linear regression.

```{r}
par(mfrow=c(2,2))
plot(lm.fit_2)
```

There is only one high leverage points.

