---
title: "Homework 2 - Q7"
author: "Srijan K. Pal"
date: "2023-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

13.(a)
```{r}
set.seed(1)
x = rnorm(100)
```

13.(b)
```{r}
eps = rnorm(100, 0, sqrt(0.25))
```

13.(c)
```{r}
y = -1+(0.5*x)+eps
```

y is of length 100.

B0 = -1, B1 = 0.5

13.(d)
```{r}
plot(x, y)
```

There is a possibility that the relationship between x and y is linear.

13.(e)
```{r}
lm.fit = lm(y~x)
summary(lm.fit)
```

Predicted coefficients: B0 = -1.01885, B1 = 0.49947

Both the predicted B0 and B1 are very close to the actual values.

The model has a large F-static with a very low p-value, so the null hypothesis can be neglected.

13.(f)
```{r}
plot(x,y)
abline(lm.fit, lwd=3, col=2)
abline(-1, 0.5, lwd=3, col=3)
legend(-1, legend = c("model fit", "pop. regression"), col=2:3, lwd=2)
```


13.(g)
```{r}
lm.fit = lm(y~x+I(x^2))
summary(lm.fit)
```

There is evidence that model fit has increased over the training data given the slight increase in R-squared and RSE. Although, the p-value and the t-statistic suggests thet there is not a relationship between y and x^2. 
